\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-19 chapters/3_algorithm.tex
Finalize cremi results section

\begin{figure}
\centering
        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_no_constr.pdf}
        \caption{No constraints}\label{subfig:no_constraints}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
        \caption{With constraints}\label{subfig:with_constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}
\begin{algorithm}[t]
  \caption{\algname{}: Generalized Algorithm for Signed Graph Agglomerative Clustering}
   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ with each node in its own cluster
      \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
      % \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      % \State Sort edges in priority queue (PQ) in descending order of absolute weight $|\cost_e|=|w^+_e - w^-_e|$ 
      % \State
      \Repeat
        \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
        % \State
        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
          \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
        % \State
        \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
        \EndIf
      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters are constrained\big]}
        % \If{({\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
        %   \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
        %   \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
        %     % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
        %     \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
        %   \EndFor
        % \EndIf
        % \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
        %   \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
        % \EndIf

@@

\subsection{\algname{}: Generalized Algorithm for Signed Graph Agglomerative Clustering} \label{sec:algorithm}

\TODO{mention detailed pseudocode} The proposed \algname{} Algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters. It starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

@@

In Appendix \ref{sec:detailed_impl} we comment on the algorithm \UPDATE{computational complexity $\mathcal{O}(N^2 \log N)$} and present an efficient implementation based on an edge contraction algorithm combined with a priority queue.

>>>>

\begin{figure}
\centering
        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_no_constr.pdf}
        \caption{No constraints}\label{subfig:no_constraints}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
        \caption{With constraints}\label{subfig:with_constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}
\begin{algorithm}[t]
  \caption{\algname{}: Generalized Algorithm for Agglomerative Signed Graph Partitioning}
   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ with each node in its own cluster
      \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
      % \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      % \State Sort edges in priority queue (PQ) in descending order of absolute weight $|\cost_e|=|w^+_e - w^-_e|$ 
      % \State
      \Repeat
        \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
        % \State
        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
          \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
        % \State
        \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
        \EndIf
      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters are constrained\big]}
        % \If{({\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
        %   \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
        %   \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
        %     % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
        %     \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
        %   \EndFor
        % \EndIf
        % \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
        %   \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
        % \EndIf

@@

\subsection{\algname{}: Generalized Algorithm for Agglomerative Signed Graph Partitioning} \label{sec:algorithm}

In Algorithm \ref{main_alg}, we provide a simplified pseudo-code for the proposed \algname{} algorithm that is based on a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters. It starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

@@

In Appendix \ref{sec:detailed_impl}, we comment on the algorithm computational complexity $\mathcal{O}(N^2 \log N)$ and present our efficient implementation given by the edge contraction Algorithm \ref{detailed_alg} using a priority queue.

### 2019-05-19 chapters/5_experiments_noise.tex
Finalize cremi results section

\subsection{Results and discussion}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested methods on the predictions of our CNN. 
The poor scores achieved by THRESH highlight the difficulty of the task. On the other hand, \algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage). The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem. 
In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
Our hypothesis to explain this superior performances it that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account. It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error. 
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.

\textbf{Noise experiments } In order to highlight the properties of each \algname{} algorithm and  perform an in-depth comparison that is as quantitative as possible, we run an additional set of experiments where we perturbed the CNN predictions with noise. Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences.  
Fig. \ref{fig:noise_plots} summarize our 12000 noise experiments: we focused on the best performing linkage criteria, i.e. \emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise, both with and without use of long-range connections in the grid-graph. % In Fig. \ref{fig:noise_plots}, we used a merge-biased noise decreasing boundary evidence. See Fig. \ref{fig:noise_split} in Appendix for a split-biased version.

\textbf{Average and Abs Max linkage } Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and that is the one benefiting more from additional long-range edge connections. Other versions using cannot-link constraints generally lead to an over-segmentation, but are robust to ``leaks through holes'' given by missing boundary evidence. The greedy \emph{absolute maximum} linkage proposed by \cite{wolf2018mutex} is the least robust to noise, but, as we show in Table \ref{tab:full_cremi_results}, it represents an efficient and considerably faster option.

\textbf{Sum linkage } The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq. \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}. Nevertheless, in more challenging parts of the data (see Fig. \ref{fig:cremi_comparison}) or in the presence of noise, it often incorrectly merge regions together, leading to more unbalanced graph partitioning. In these cases, the use of cannot-link constraints or a more robust average linkage are preferable.  
In Fig. \ref{fig:cremi_comparison}, we highlight some failure cases of the different agglomerative algorithms included in our framework.

>>>>

\subsection{Results and discussion}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested post-processing methods applied to the predictions of our model. 
% The poor scores achieved by THRESH highlight the difficulty of the task. 
\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage). The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem. 
In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
Our hypothesis to explain this superior performances it that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account. It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error. 
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.

\textbf{Noise experiments } Fig. \ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework. Additionally, we run a set of experiments where the CNN predictions are perturbed by noise, in order to highlight the properties of each \algname{} algorithm and perform an in-depth comparison that is as quantitative as possible. Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences.  
Fig. \ref{fig:noise_plots} summarize our 12000 noise experiments: we focused on the best performing linkage criteria, i.e. \emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise, both with and without use of long-range connections in the grid-graph. % In Fig. \ref{fig:noise_plots}, we used a merge-biased noise decreasing boundary evidence. See Fig. \ref{fig:noise_split} in Appendix for a split-biased version.

\textbf{Average and Abs Max linkage } Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and the one that benefits the most from using the long-range CNN predictions. On the other hand, it is not a surprise that the \emph{Abs Max} statistic proposed by \cite{wolf2018mutex} is less robust to noise than the \emph{Average} linkage, but, as we show in the Appendix \TODO{Table \ref{tab:full_cremi_results}}, \emph{Abs Max} represents a valid and considerably faster option. 
Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights, then \algname{} with cannot-link constraints shows a clear tendency to over-cluster.

\textbf{Sum linkage } 
% The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq. \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}. 
All our experiments, as well as the examples in Fig. \ref{fig:cremi_comparison}, show that \algname{} with \emph{Sum} linkage is the algorithm with the highest probability of under-clustering and incorrectly merging segments. This is strongly related to the  empirical observation highlighted in Fig. \ref{fig:intro_figure}, where it is shown that the agglomeration order given by \algname{} with \emph{Sum} linkage is clearly different as compared to those given by other linkage criteria like \emph{Average} or \emph{Abs Max}. Particularly, a \emph{Sum} statistic tends to grow clusters one after the other. The intuitive explanation behind this is the following: initially, most of the infra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning. On the other hand, other linkage criteria grow clusters of similar sizes in parallel and accumulate more valuable statistics between the clusters.
